Dusty Days and a Vibrio Craze: The Influence of Saharan Dust Deposition on Microbial Communities in High Nutrient Coastal Waters 

### 2023-05-04 products/manuscript/Manuscript.qmd
Final Edits :)

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 3: Envonmental parameters across daily time series with color by site(Blind Oso = green, Canals = red, and the Gulf = Blue"}
knitr::include_graphics(here("results", "plots", "env.png"))
```

@@

The annual dust data set indicates a period of slightly elevated AOD (0.16) on the 5th of July, prior to sampling. This light dust period could have the potential to impact initial *Vibrio* levels at the beginning of the time series, which may serve as an explanation for initial higher *Vibrio* gene copies/mL at the Canals, and why the correlation between dust and *Vibrio* gene copies/mL was so high at this site. Future work should expand upon the temporal resolution, allowing for an extended period of low dust AOD prior to sampling.

>>>>

```{r, echo=FALSE, message=FALSE, fig.cap="Figure 3: Envonmental parameters across daily time series with color by site (Blind Oso = green, Canals = red, and the Gulf = Blue)"}
knitr::include_graphics(here("results", "plots", "env.png"))
```

@@

The annual dust data set indicates a period of slightly elevated AOD (0.16) on the 5th of July, prior to sampling (SI). This light dust period could have the potential to impact initial *Vibrio* levels at the beginning of the time series, which may serve as an explanation for initial higher *Vibrio* gene copies/mL at the Canals, and why the correlation between dust and *Vibrio* gene copies/mL was so high at this site. Future work should expand upon the temporal resolution, allowing for an extended period of low dust AOD prior to sampling.
